\documentclass[journal]{IEEEtran}
\usepackage{fullpage,enumitem,amsfonts,amsmath,amssymb,graphicx}

\begin{document}
\title{Personal Legal Counselor and Interpreter of the Law via Machine Learning}
\author{Tai Guo, Derek Yan\\
\{taig, zhyan\}@stanford.edu}
\markboth{Final report for CS221, Fall 2014}
{Shell \MakeLowercase{\textit{et al.}}: Personal Legal Counselor and Interpreter of the Law via Machine Learning}
\maketitle

\begin{abstract}
We predicted the likelihood of winning a legal dispute based on results from past cases. We collected over 5000 legal proceedings from the past in the form of case briefs. Consequentely, we performed word feature extractions through NLP on the case briefs along with the binary labels that indicated whether a case was won or lost. We used SVM and logistic regression for the prediction. Lastly, we achieved a test accuracy of 62\% using both algorithms.
\end{abstract}

\begin{keywords}
Law, machine learning, case briefs, court cases.
\end{keywords}

\section{Introduction}
\IEEEPARstart{``T} he first thing we do, let’s kill all the lawyers'' - William Shakespeare, 2 Henry VI, 4.2.59. Any major transaction, legal procedure, patent dispute always require an attorney-at-law in the due process. However, the cost of seeking such legal counseling or hiring a lawyer is often astronomical for everyday people. Even though there are always legitimate cases of people who fall victims to unjust treatment; contractual violation; patent infringement; and etc, these victims often do not have the financial resources to seek justice through legal counseling. Our team looked to create an interactive legal counselor and interpreter of the law for the disenfranchised. Users would input their legal dispute in text format. The tool would then predict whether the case is winnable or not.

\section{Related Work}
The goal of this project is to predict the outcome of a legal proceedings or class actions based on previous court proceedings. Legal advice is often very expensive, which would make a tool that provides free counseling by examining previous cases very useful to anyone with a legal dispute. In addition, this application would give user an impartial assessment of the chances they have of winning their case.

\section{Data Set}
The goal of this project is to predict the outcome of a legal proceedings or class actions based on previous court proceedings. Legal advice is often very expensive, which would make a tool that provides free counseling by examining previous cases very useful to anyone with a legal dispute. In addition, this application would give user an impartial assessment of the chances they have of winning their case.

\section{Methodology}
The goal of this project is to predict the outcome of a legal proceedings or class actions based on previous court proceedings. Legal advice is often very expensive, which would make a tool that provides free counseling by examining previous cases very useful to anyone with a legal dispute. In addition, this application would give user an impartial assessment of the chances they have of winning their case.

\section{Results}
The goal of this project is to predict the outcome of a legal proceedings or class actions based on previous court proceedings. Legal advice is often very expensive, which would make a tool that provides free counseling by examining previous cases very useful to anyone with a legal dispute. In addition, this application would give user an impartial assessment of the chances they have of winning their case.

\section{Conclusion}
The conclusion goes here.
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

\end{document}

